### 2022-06-24 Report/manuscript.tex
Updating report

\usepackage{cite}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{amstext,amsmath,amssymb}
\usepackage[shortlabels]{enumitem}

@@

\sloppy

@@

    \begin{figure}[ht!]
        \centering 
        \includegraphics[width=0.75\linewidth]{figs/hw0a1.png} \par 
        \caption{Monter Carlo Experiment with 5000.}
        \label{fig:hw0a1} 
    \end{figure}

    \begin{figure}[ht!]
        \centering 
        \includegraphics[width=0.75\linewidth]{figs/hw0a2.png} \par 
        \caption{Monter Carlo Experiment with 10000 runs.}
        \label{fig:hw0a2} 
    \end{figure}

    \subsection*{Show that $\text{eig}(\boldsymbol{A} \otimes \boldsymbol{B}) = \text{eig}(\boldsymbol{A}) \otimes \text{eig}(\boldsymbol{B})$}

@@

@@

@@

    \begin{figure}[ht!]
        \centering 
        \includegraphics[width=0.75\linewidth]{figs/hw1a1.png} \par 
        \caption{Monter Carlo Experiment with 1000 runs.}
        \label{fig:hw1a1} 
    \end{figure}

@@

    \begin{figure}[ht!]
        \centering 
        \includegraphics[width=0.75\linewidth]{figs/hw1a2.png} \par 
        \caption{Monter Carlo Experiment with 1000 runs.}
        \label{fig:hw1a2} 
    \end{figure}

@@

    \begin{figure}[ht!]
        \centering 
        \includegraphics[width=0.75\linewidth]{figs/hw1a3.png} \par 
        \caption{Monter Carlo Experiment with 1000 runs.}
        \label{fig:hw1a3} 
    \end{figure}

@@

    In Figures \ref{fig:hw2a1} and \ref{fig:hw2a2} we can see the processing time for the considered methods to compute the pseudoinverse of a Khatri-Rao product for the cases
    where we have two and four columns in each matrix. To draw the curves it was implemented a Monte Carlo Experiment with only 250 runs for each value $N$ of rows with $N \in \{2, 4, 8, 16, 32, 64\}$.
    For both cases we can see a clear advantage in using the third method as the dimmensions of the matrices increases. In a similar maner, we can also observe that the second method is a bit better than the first however 
    not as good as the third. To see a better behavior for these methods it should be necessary to increase the number of rows to better analyse the advantages of each one, however due to technical constraints 
    I could not increase as much as I wanted.

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

    \subsection*{Implementation KPSVD}

@@

    In the example is considered that the original matrix has a full rank equals to 9, then two approximations using the KPSVD are provided: One using the full-rank approximation and other using a r-rank approximation $(r < 9)$. 
    The NMSE between some approximations and its original matrix are provided in the sequence

    \begin{table}[ht!]
        \centering
        \begin{tabular}{|l|l|l|l|l|}
        \hline
        Full Rank & Rank = $7$ & Rank = $5$ & Rank = $3$ & Rank = $1$ \\ \hline
        -604.8023 & -51.3722 & -26.7589 & -16.9054 & -6.3068 \\ \hline
        \end{tabular}
    \end{table}

    \subsection*{Validation of KPSVD}

>>>>

\usepackage{cite}
\usepackage{graphicx,color}
\usepackage{fancyhdr}
\usepackage{amstext,amsmath,amssymb}
\usepackage[shortlabels]{enumitem}

\usepackage{subcaption}
\usepackage{mwe}

@@

\sloppy
\definecolor{lightgray}{gray}{0.5}
\setlength{\parindent}{0pt}

@@

    \begin{figure}[ht!]
        \centering 
        \includegraphics[width=0.65\linewidth]{figs/hw0a1.png} \par 
        \caption{Monter Carlo Experiment with 5000.}
        \label{fig:hw0a1} 
    \end{figure}

    \begin{figure}[ht!]
        \centering 
        \includegraphics[width=0.65\linewidth]{figs/hw0a2.png} \par 
        \caption{Monter Carlo Experiment with 10000 runs.}
        \label{fig:hw0a2} 
    \end{figure}

    \newpage
    \subsection*{Show that $\text{eig}(\boldsymbol{A} \otimes \boldsymbol{B}) = \text{eig}(\boldsymbol{A}) \otimes \text{eig}(\boldsymbol{B})$}

@@

    \subsection*{Produced Algorithm}

    \begin{verbatim}
        %% ----- Homework 0 ----- %%
        clc;
        clear;
        close all;
        N = [1 2 3 4 5 6 7 8];
        time1 = zeros(length(N),1);
        time2 = zeros(length(N),1);
        for nn = 1:length(N)
            for mc = 1:5000
                A = randn(N(nn),N(nn)) + 1j*randn(N(nn),N(nn));
                B = randn(N(nn),N(nn)) + 1j*randn(N(nn),N(nn));
                tic;
                inv(tensor.mtx_prod_kron(A,B));
                aux = toc;
                time1(nn,1) = time1(nn,1) + aux;
                tic;
                tensor.mtx_prod_kron(inv(A),inv(B));
                aux = toc;
                time2(nn,1) = time2(nn,1) + aux;
            end
        end
        time1 = time1/5000;
        time2 = time2/5000;
        figure
        txt = ['(\bf A_{N \times N} \otimes B_{N \times N})^{-1}'];
        semilogy(N,time1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
            "markersize", 8, "DisplayName", txt);
        hold on;
        txt = ['\bf A^{-1}_{N \times N} \otimes B^{-1}_{N \times N}'];
        semilogy(N,time2,'-o','color', [0.8500 0.3250 0.0980], "linewidth", 2,...
            "markersize", 8, "DisplayName", txt);
        hold off;
        title(['Performance of inverse operation'])
        xlabel('Number of columns')
        ylabel('Time (s)')
        legend_copy = legend("location", "northwest");
        set(legend_copy,'Interpreter','tex','location','northwest',"fontsize", 12)
        grid on;
        saveas(gcf,'hw0a1.png')
        N = 2;
        K = [1 2 3 4 5 6 7 8 9 10];
        time1 = zeros(length(K),1);
        time2 = zeros(length(K),1);
        for kk = 1:length(K)
            for mc = 1:1000
                tic;
                for ii = 1:K(kk)    
                    if ii == 1
                        A1 = randn(N,N) + 1j*randn(N,N); 
                        continue
                    else
                        A2 = randn(N,N) + 1j*randn(N,N);
                        A1 = tensor.mtx_prod_kron(A1,A2);
                    end    
                end
                inv(A1);
                aux = toc;
                time1(kk,1) = time1(kk,1) + aux;

                tic;
                for ii = 1:K(kk)    
                    if ii == 1
                        A1 = randn(N,N) + 1j*randn(N,N); 
                        continue
                    else
                        A2 = randn(N,N) + 1j*randn(N,N);
                        A1 = tensor.mtx_prod_kron(inv(A1),inv(A2));
                    end    
                end
                aux = toc;
                time2(kk,1) = time2(kk,1) + aux;
            end
        end
        time1 = time1/1000;
        time2 = time2/1000;
        figure
        txt = ['\bf (\otimes^{K}_{i = 1}A^{(i)}_{4 \times 4})^{-1}'];
        semilogy(K,time1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
            "markersize", 8, "DisplayName", txt);
        hold on;
        txt = ['\bf \otimes^{K}_{i = 1}(A^{(i)}_{4 \times 4})^{-1}'];
        semilogy(K,time2,'-o','color', [0.8500 0.3250 0.0980], "linewidth", 2,...
            "markersize", 8, "DisplayName", txt);
        hold off;
        title(['Multiple Kronecker products performance'])
        xlabel('Number of products')
        ylabel('Time (s)')
        legend_copy = legend("location", "northwest");
        set(legend_copy,'Interpreter','tex','location','northwest',"fontsize", 12)
        grid on;
        saveas(gcf,'hw0a2.png')
    \end{verbatim}

@@

    In Figure \ref{fig:hw1a1}, \ref{fig:hw1a2} and \ref{fig:hw1a3} I compare my implemention of Hadarmard, Kronecker and Khatri-Rao Products with the ones availables in the TensorLab package.
    As we can the only case where my function have shown an almost equal performance to the benchmark was the one where I do the Kronecker Product. The other two functions are far from the ideal
    performance offered by the TensorLab package. This could probably explained because I did not take full advantage of the vectorization that MATLAB offers when I was creating those two algorithms.

@@

    \begin{figure}[ht!]
        \centering 
        \includegraphics[width=0.65\linewidth]{figs/hw1a1.png} \par 
        \caption{Monter Carlo Experiment with 1000 runs.}
        \label{fig:hw1a1} 
    \end{figure}

@@

    \begin{figure}[ht!]
        \centering 
        \includegraphics[width=0.65\linewidth]{figs/hw1a2.png} \par 
        \caption{Monter Carlo Experiment with 1000 runs.}
        \label{fig:hw1a2} 
    \end{figure}

@@

    \begin{figure}[ht!]
        \centering 
        \includegraphics[width=0.65\linewidth]{figs/hw1a3.png} \par 
        \caption{Monter Carlo Experiment with 1000 runs.}
        \label{fig:hw1a3} 
    \end{figure}

    \newpage
    \subsection*{Produced Algorithm}

    \begin{verbatim}
        %% Hadamard Product

        % This function computes the Hadarmard Product of two given matrices.   
        % Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
        % Created: January 2022

        function C = mtx_prod_had(A,B)

            [ia,ja] = size(A);
            [ib,jb] = size(B);

            if (ia ~= ib) || (ja~=jb)
                disp('Invalid Matrices!')
                return;
            else
                C = A.*B;
                %C = zeros(ia,ja);
                %for i = 1:ia 
                    %for j = 1:ja
                        %C(i,j) = A(i,j)*B(i,j);
                    %end
                %end
            end
        end

        %% Kronecker Product

        % This function computes the Kronecker Product of two given matrices. 
        % Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
        % Created: January 2022

        function C = mtx_prod_kron(A,B)

            [ia,ja] = size(A);
            [ib,jb] = size(B);

            A = repelem(A,ib,jb);
            B = repmat(B,[ia ja]);
            C = A.*B;

        end

        %% Khatri-Rao Product

        % This function computes the Khatri-Rao Product of two given matrices. 
        % Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
        % Created: January 2022

        function C = mtx_prod_kr(A,B)
            [ia,ja] = size(A);
            [ib,jb] = size(B);

            if (ja~=jb)
                disp('Invalid Matrices!')
                return;
            else
                C = zeros(ia*ib,ja);
                for j = 1:ja
                    C(:,j) = tensor.mtx_prod_kron(A(:,j),B(:,j));
                end
            end
        end

        %% ----- Homework 1 ----- %%
        clc;
        clear;
        close all;

        N = [2 4 8 16 32 64 128];
        time1 = zeros(length(N),1);
        time2 = zeros(length(N),1);
        for nn = 1:length(N)
            for mc = 1:1000
                A = randn(N(nn),N(nn)) + 1j*randn(N(nn),N(nn));
                B = randn(N(nn),N(nn)) + 1j*randn(N(nn),N(nn));
                tic;
                A.*B;
                aux = toc;
                time1(nn,1) = time1(nn,1) + aux;
                tic;
                tensor.mtx_prod_had(A,B);
                aux = toc;
                time2(nn,1) = time2(nn,1) + aux;
            end
        end
        time1 = time1/1000;
        time2 = time2/1000;

        figure
        txt = ['Native Function'];
        semilogy(N,time1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
            "markersize", 8, "DisplayName", txt);
        hold on;
        txt = ['Author Function'];
        semilogy(N,time2,'-o','color', [0.8500 0.3250 0.0980], "linewidth", 2,...
            "markersize", 8, "DisplayName", txt);
        hold off;
        title(['Hadamard product performance'])
        xlabel('Number of columns')
        ylabel('Time (s)')
        legend_copy = legend("location", "southeast");
        set(legend_copy,'Interpreter','tex','location','southeast',"fontsize", 12)
        grid on;
        saveas(gcf,'hw1a1.png')

        N = [2 4 8 16 32 64];
        time1 = zeros(length(N),1);
        time2 = zeros(length(N),1);
        for nn = 1:length(N)
            for mc = 1:1000
                A = randn(N(nn),N(nn)) + 1j*randn(N(nn),N(nn));
                B = randn(N(nn),N(nn)) + 1j*randn(N(nn),N(nn));
                tic;
                kron(A,B);
                aux = toc;
                time1(nn,1) = time1(nn,1) + aux;
                tic;
                tensor.mtx_prod_kron(A,B);
                aux = toc;
                time2(nn,1) = time2(nn,1) + aux;
            end
        end
        time1 = time1/1000;
        time2 = time2/1000;

        figure
        txt = ['Native Function'];
        semilogy(N,time1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
            "markersize", 8, "DisplayName", txt);
        hold on;
        txt = ['Author Function'];
        semilogy(N,time2,'-o','color', [0.8500 0.3250 0.0980], "linewidth", 2,...
            "markersize", 8, "DisplayName", txt);
        hold off;
        title(['Kronecker product performance'])
        xlabel('Number of columns')
        ylabel('Time (s)')
        legend_copy = legend("location", "northwest");
        set(legend_copy,'Interpreter','tex','location','northwest',"fontsize", 12)
        grid on;
        saveas(gcf,'hw1a2.png')

        N = [2 4 8 16 32 64];
        time1 = zeros(length(N),1);
        time2 = zeros(length(N),1);
        for nn = 1:length(N)
            for mc = 1:1000
                A = randn(N(nn),N(nn)) + 1j*randn(N(nn),N(nn));
                B = randn(N(nn),N(nn)) + 1j*randn(N(nn),N(nn));
                tic;
                kr(A,B);
                aux = toc;
                time1(nn,1) = time1(nn,1) + aux;
                tic;
                tensor.mtx_prod_kr(A,B);
                aux = toc;
                time2(nn,1) = time2(nn,1) + aux;
            end
        end
        time1 = time1/1000;
        time2 = time2/1000;

        figure
        txt = ['Native Function'];
        semilogy(N,time1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
            "markersize", 8, "DisplayName", txt);
        hold on;
        txt = ['Author Function'];
        semilogy(N,time2,'-o','color', [0.8500 0.3250 0.0980], "linewidth", 2,...
            "markersize", 8, "DisplayName", txt);
        hold off;
        title(['Khatri-Rao product performance'])
        xlabel('Number of columns')
        ylabel('Time (s)')
        legend_copy = legend("location", "northwest");
        set(legend_copy,'Interpreter','tex','location','northwest',"fontsize", 12)
        grid on;
        saveas(gcf,'hw1a3.png')
    \end{verbatim}

@@

    In Figures \ref{fig:hw2a1} and \ref{fig:hw2a2} we can see the processing time for the considered methods to compute the pseudoinverse of a Khatri-Rao product for the cases
    where we have two and four columns in each matrix. To draw the curves it was implemented a Monte Carlo Experiment with only 250 runs for each value $N$ of rows with $N \in \{2, 4, 8, 16, 32, 64\}$.
    For both cases we can see a clear advantage in using the third method as the dimmensions of the matrices increases. In a similar maner, we can also observe that the second method is a bit better than the first however 
    not as good as the third. To see a better behavior for these methods it should be necessary to increase the number of rows to better analyse the advantages of each one, however due to technical constraints 
    I could not increase as much as I wanted. In the sequence we can see the definition of each implemented method.

@@

    In Figure \ref{fig:hw2a3} we analyze the behavior of the Khatri-Rao product when sequential products are taken. As we can see it is an exponencial curve since after every product we will have matrices with analyse
    increasing dimmensions. Thus, when we do need to use consecutive Khatri-Rao products we should seek a way to simplify the operation by using algebraic manipulations.

@@

    \newpage
    \subsection*{Produced Algorithm}

    \begin{verbatim}
        %% ----- Homework 2 ----- %%
        clc;
        clear;
        close all;

        R = 2;
        I = [2 4 8 16 32 64];
        time1 = zeros(length(I),1);
        time2 = zeros(length(I),1);
        time3 = zeros(length(I),1);
        for ii = 1:length(I)
            for mc = 1:250
                A = randn(I(ii),I(ii)) + 1j*randn(I(ii),I(ii));
                B = randn(I(ii),I(ii)) + 1j*randn(I(ii),I(ii));
                tic;
                pinv(tensor.mtx_prod_kr(A,B));
                aux = toc;
                time1(ii,1) = time1(ii,1) + aux;
                tic;
                (tensor.mtx_prod_kr(A,B).'*tensor.mtx_prod_kr(A,B))...
                    \(tensor.mtx_prod_kr(A,B).');
                aux = toc;
                time2(ii,1) = time2(ii,1) + aux;
                tic;
                tensor.mtx_prod_had((A.'*A),(B.'*B))\(tensor.mtx_prod_kr(A,B).');
                aux = toc;
                time3(ii,1) = time3(ii,1) + aux;
            end
        end
        time1 = time1/250;
        time2 = time2/250;
        time3 = time3/250;

        figure
        txt = ['1st Method'];
        plot(I,time1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
            "markersize", 8, "DisplayName", txt);
        hold on;
        txt = ['2nd Method'];
        plot(I,time2,'-d','color', [0.8500 0.3250 0.0980], "linewidth", 2,...
            "markersize", 8, "DisplayName", txt);
        hold on;
        txt = ['3rd Method'];
        plot(I,time3,'-d','color', [0.4660 0.6740 0.1880], "linewidth", 2,...
            "markersize", 8, "DisplayName", txt);
        hold off;
        title(['Khatri-Rao product performance considering 2 columns'])
        xlabel('Number of rows')
        ylabel('Time (s)')
        legend_copy = legend("location", "northwest");
        set(legend_copy,'Interpreter','tex','location','northwest',"fontsize", 12)
        grid on;
        saveas(gcf,'hw2a1.png')

        R = 4;
        I = [2 4 8 16 32 64];
        time1 = zeros(length(I),1);
        time2 = zeros(length(I),1);
        time3 = zeros(length(I),1);
        for ii = 1:length(I)
            for mc = 1:250
                A = randn(I(ii),I(ii)) + 1j*randn(I(ii),I(ii));
                B = randn(I(ii),I(ii)) + 1j*randn(I(ii),I(ii));
                tic;
                pinv(tensor.mtx_prod_kr(A,B));
                aux = toc;
                time1(ii,1) = time1(ii,1) + aux;
                tic;
                (tensor.mtx_prod_kr(A,B).'*tensor.mtx_prod_kr(A,B))...
                    \(tensor.mtx_prod_kr(A,B).');
                aux = toc;
                time2(ii,1) = time2(ii,1) + aux;
                tic;
                tensor.mtx_prod_had((A.'*A),(B.'*B))\(tensor.mtx_prod_kr(A,B).');
                aux = toc;
                time3(ii,1) = time3(ii,1) + aux;
            end
        end
        time1 = time1/250;
        time2 = time2/250;
        time3 = time3/250;

        figure
        txt = ['1st Method'];
        plot(I,time1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
            "markersize", 8, "DisplayName", txt);
        hold on;
        txt = ['2nd Method'];
        plot(I,time2,'-d','color', [0.8500 0.3250 0.0980], "linewidth",...
            2, "markersize", 8, "DisplayName", txt);
        hold on;
        txt = ['3rd Method'];
        plot(I,time3,'-d','color', [0.4660 0.6740 0.1880], "linewidth",...
            2, "markersize", 8, "DisplayName", txt);
        hold off;
        title(['Khatri-Rao product performance considering 4 columns'])
        xlabel('Number of rows')
        ylabel('Time (s)')
        legend_copy = legend("location", "northwest");
        set(legend_copy,'Interpreter','tex','location','northwest',"fontsize", 12)
        grid on;
        saveas(gcf,'hw2a2.png')

        I = 4;
        R = 2;
        N = [2 4 6 8];
        time1 = zeros(length(N),1);
        time2 = zeros(length(N),1);
        for nn = 1:length(N)
            for mc = 1:250 
                tic;
                for ii = 1:N(nn)
                    if ii == 1
                        A1 = randn(I,R) + 1j*randn(I,R); 
                        continue
                    else
                        A2 = randn(I,R) + 1j*randn(I,R);
                        A1 = tensor.mtx_prod_kron(A1,A2);
                    end    
                end
                aux = toc;
                time1(nn,1) = time1(nn,1) + aux;
            end
        end
        time1 = time1/250;

        figure
        txt = ['\bf \diamond^{N}_{n = 1} (A^{(n)}_{4 \times 2})'];
        semilogy(N,time1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
            "markersize", 8, "DisplayName", txt);
        title(['Multiple Khatri-Rao products performance'])
        xlabel('Number of Products')
        ylabel('Time (s)')
        legend_copy = legend("location", "northwest");
        set(legend_copy,'Interpreter','tex','location','northwest',"fontsize", 12)
        grid on;
        saveas(gcf,'hw2a3.png')
    \end{verbatim}

@@

    The LSKRF algorithm aims to solve the following estimation problem

@@

    and by implementing the algorithm it was possible to reach the following table of NMSE (dB) values using the validation files

@@

    as we can see the estimation of the matrix $\boldsymbol{X}$ is perfect, but the estimated factor matrices are far from the original ones. This is simply explained by 
    the scale ambiguity intrinsic to the LSKRF. This could be eliminated if we assume previous knowledge of either the structure of the factor matrices or some of their elements.

@@

    In Figure \ref{fig:hw3} the Monte Carlo Experiment is used to draw the curves for two different scenarios: $(I,J,R) = (10,10,4)$ and $(I,J,R) = (30,10,4)$. 
    As we can observe the best performance is the one where the algorithm have fewer elements to estimate. This is to be expected since the noise will have a lot less
    components that could potentially harm the performance of the LSKRF.

@@

    \newpage
    \subsection*{Produced Algorithm}

    \begin{verbatim}
        %% Least-Squares Khatri-Rao Factorization (LSKRF)

        % This function computes the LSKRF of a given matrix.   
        % Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
        % Created: February 2022

        function [Ahat,Bhat] = LSKRF(C,ia,ib)
            [~, jc] = size(C);

            Ahat = complex(zeros(ia,jc),0);
            Bhat = complex(zeros(ib,jc),0);

            for j = 1:jc
                Cp = C(:,j);
                Cp = reshape(Cp, [ib ia]);
                [U,S,V] = svd(Cp);
                Ahat(:,j) = sqrt(S(1,1)).*conj(V(:,1));
                Bhat(:,j) = sqrt(S(1,1)).*U(:,1);
            end
        end

        %% ----- Homework 3 ----- %%
        clc;
        clear;
        close all;

        A = randn(4,2) + 1j*randn(4,2);
        B = randn(6,2) + 1j*randn(6,2);
        X = tensor.mtx_prod_kr(A,B);
        [Ahat,Bhat] = tensor.LSKRF(X,4,6);
        Xhat = tensor.mtx_prod_kr(Ahat,Bhat);

        disp('Checking the NMSE (dB) between the original matrix X and its'... 
            'reconstruction with LSKRF:')
        nmsex = (norm(X- Xhat,'fro')^2)/(norm(X,'fro')^2);
        nmsex = 20*log10(nmsex)
        disp('Checking the NMSE (dB) between the original matrix A and its'...
            'estimation:')
        nmsea = (norm(A- Ahat,'fro')^2)/(norm(A,'fro')^2);
        nmsea = 20*log10(nmsea)
        disp('Checking the NMSE (dB) between the original matrix B and its'... 
            'estimation:')
        nmseb = (norm(B- Bhat,'fro')^2)/(norm(B,'fro')^2);
        nmseb = 20*log10(nmseb)

        I = 10;
        J = 10;
        R =  4;
        SNR = [0 5 10 15 20 25 30];
        nmse = zeros(length(SNR),1);
        for snr = 1:length(SNR)
            for mc = 1:1000
                var_noise = 1/(10^(SNR(snr)/10));
                noise = sqrt(var_noise/2)*(randn(I*J,R) + 1j*randn(I*J,R));

                A = randn(I,R) + 1j*randn(I,R);
                B = randn(J,R) + 1j*randn(J,R);
                X = tensor.mtx_prod_kr(A,B);
                X_noisy = X + noise;

                [Ahat,Bhat] = tensor.LSKRF(X_noisy,I,J);
                Xhat = tensor.mtx_prod_kr(Ahat,Bhat);
                aux = (norm(X- Xhat,'fro')^2)/(norm(X,'fro')^2);
                nmse(snr,1) = nmse(snr,1) + 20*log10(aux);
            end
        end
        nmse  = nmse/1000;

        figure
        txt = ['I = ' num2str(I), ', J = ' num2str(J), ' and R = ' num2str(R)];
        plot(SNR,nmse,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
            "markersize", 8, "DisplayName", txt);
        hold on;

        I = 30;
        J = 10;
        R =  4;
        SNR = [0 5 10 15 20 25 30];
        nmse = zeros(length(SNR),1);
        for snr = 1:length(SNR)
            for mc = 1:1000
                var_noise = 1/(10^(SNR(snr)/10));
                noise = sqrt(var_noise/2)*(randn(I*J,R) + 1j*randn(I*J,R));

                A = randn(I,R) + 1j*randn(I,R);
                B = randn(J,R) + 1j*randn(J,R);
                X = tensor.mtx_prod_kr(A,B);
                X = X + noise;

                [Ahat,Bhat] = tensor.LSKRF(X,I,J);
                Xhat = tensor.mtx_prod_kr(Ahat,Bhat);
                aux = (norm(X- Xhat,'fro')^2)/(norm(X,'fro')^2);
                nmse(snr,1) = nmse(snr,1) + 20*log10(aux);
            end
        end
        nmse  = nmse/1000;

        txt = ['I = ' num2str(I), ', J = ' num2str(J), ' and R = ' num2str(R)];
        plot(SNR,nmse,'-d','color', [0.4660 0.6740 0.1880], "linewidth", 2,...
            "markersize", 8, "DisplayName", txt);
        hold off;
        title(['LSKRF performance under imperfect scenario'])
        xlabel('SNR (dB)')
        ylabel('NMSE (dB)')
        legend_copy = legend("location", "northwest");
        set(legend_copy,'Interpreter','tex','location','northeast',"fontsize", 12)
        grid on;
        saveas(gcf,'hw3.png')
    \end{verbatim}

@@

    The LSKronF algorithm aims to solve the following estimation problem

@@

    as we can see the estimation of the matrix $\boldsymbol{X}$ is perfect, but the estimated factor matrices are far from the original ones. This is simply explained by 
    the scale ambiguity intrinsic to the LSKronF. This could be eliminated if we assume previous knowledge of either the structure of the factor matrices or some of their elements.

@@

    In Figure \ref{fig:hw4} the Monte Carlo Experiment is used to draw the curves for two different scenarios: $(I,J,P,Q) = (2,4,3,5)$ and $(I,J,P,Q) = (4,8,3,5)$. 
    As we can observe the best performance is the one where the algorithm have fewer elements to estimate. This is to be expected since the noise will have a lot less
    components that could potentially harm the performance of the LSKronF.

@@

    \newpage
    \subsection*{Produced Algorithm}

    \begin{verbatim}
        %% Least-Square Kronecker Product Factorization (LSKronF)

        % This function computes the LSKronF of a given matrix.   
        % Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
        % Created: February 2022

        function [Ahat,Bhat] = LSKronF(C,ia,ja,ib,jb)
            [ic,jc] = size(C);

            I = (ic/ia) + zeros(1,ia);
            J = (jc/ja) + zeros(1,ja);
            blocks_of_C = mat2cell(C,I,J);

            k = 1;
            Chat = complex(zeros(ib*jb,ia*ja),0);
            for j = 1:ja
                for i = 1:ia
                    vec_of_block = cell2mat(blocks_of_C(i,j));
                    vec_of_block = vec_of_block(:);
                    Chat(:,k) = vec_of_block;
                    k = k + 1;
                end
            end

            [U,S,V] = svd(Chat);
            ahat = sqrt(S(1,1)).*conj(V(:,1));
            bhat = sqrt(S(1,1)).*U(:,1);
            Ahat = reshape(ahat,[ia ja]);
            Bhat = reshape(bhat, [ib jb]);
        end

        %% ----- Homework 4 ----- %%
        clc;
        clear;
        close all;

        A = randn(4,2) + 1j*randn(4,2);
        B = randn(6,3) + 1j*randn(6,3);
        X = tensor.mtx_prod_kron(A,B);
        [Ahat,Bhat] = tensor.LSKronF(X,4,2,6,3);
        Xhat = tensor.mtx_prod_kron(Ahat,Bhat);

        disp('Checking the NMSE (dB) between the original matrix X and its'...
            'reconstruction with LSKronF:')
        nmsex = (norm(X- Xhat,'fro')^2)/(norm(X,'fro')^2);
        nmsex = 20*log10(nmsex)
        disp('Checking the NMSE (dB) between the original matrix A and its'...
            'estimation:')
        nmsea = (norm(A- Ahat,'fro')^2)/(norm(A,'fro')^2);
        nmsea = 20*log10(nmsea)
        disp('Checking the NMSE (dB) between the original matrix B and its'...
            'estimation:')
        nmseb = (norm(B- Bhat,'fro')^2)/(norm(B,'fro')^2);
        nmseb = 20*log10(nmseb)

        I = 2;
        J = 4;
        P = 3;
        Q = 5;
        SNR = [0 5 10 15 20 25 30];
        nmse = zeros(length(SNR),1);
        for snr = 1:length(SNR)
            for mc = 1:1000
                var_noise = 1/(10^(SNR(snr)/10));
                noise = sqrt(var_noise/2)*(randn(I*J,P*Q) + 1j*randn(I*J,P*Q));

                A = randn(I,P) + 1j*randn(I,P);
                B = randn(J,Q) + 1j*randn(J,Q);
                X = tensor.mtx_prod_kron(A,B);
                X_noisy = X + noise;

                [Ahat,Bhat] = tensor.LSKronF(X_noisy,I,P,J,Q);
                Xhat = tensor.mtx_prod_kron(Ahat,Bhat);
                aux = (norm(X- Xhat,'fro')^2)/(norm(X,'fro')^2);
                nmse(snr,1) = nmse(snr,1) + 20*log10(aux);
            end
        end
        nmse  = nmse/1000;

        figure
        txt = ['I = ' num2str(I), ', J = ' num2str(J), ', P = ' num2str(P),...
            ' and Q = ' num2str(Q)];
        plot(SNR,nmse,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
            "markersize", 8, "DisplayName", txt);
        hold on;

        I = 4;
        J = 8;
        P = 3;
        Q = 5;
        SNR = [0 5 10 15 20 25 30];
        nmse = zeros(length(SNR),1);
        for snr = 1:length(SNR)
            for mc = 1:1000
                var_noise = 1/(10^(SNR(snr)/10));
                noise = sqrt(var_noise/2)*(randn(I*J,P*Q) + 1j*randn(I*J,P*Q));

                A = randn(I,P) + 1j*randn(I,P);
                B = randn(J,Q) + 1j*randn(J,Q);
                X = tensor.mtx_prod_kron(A,B);
                X = X + noise;

                [Ahat,Bhat] = tensor.LSKronF(X,I,P,J,Q);
                Xhat = tensor.mtx_prod_kron(Ahat,Bhat);
                aux = (norm(X- Xhat,'fro')^2)/(norm(X,'fro')^2);
                nmse(snr,1) = nmse(snr,1) + 20*log10(aux);
            end
        end
        nmse  = nmse/1000;

        txt = ['I = ' num2str(I), ', J = ' num2str(J), ', P = ' num2str(P),...
            ' and Q = ' num2str(Q)];
        plot(SNR,nmse,'-d','color', [0.4660 0.6740 0.1880], "linewidth", 2,...
            "markersize", 8, "DisplayName", txt);
        hold off;
        title(['LSKronF performance under imperfect scenario'])
        xlabel('SNR (dB)')
        ylabel('NMSE (dB)')
        legend_copy = legend("location", "northwest");
        set(legend_copy,'Interpreter','tex','location','northeast',"fontsize", 12)
        grid on;
        saveas(gcf,'hw4.png')
    \end{verbatim}

@@

    \subsection*{Implementation and Validation of KPSVD}

    The KPSVD algorithm aims to solve the following estimation problem

@@

    Since a validation file was not available I decided to create my own validation by generating a full-rank matrix with $R = 9$ and in sequence two approximations using my KPSVD implementation are provided: \
    One using the full-rank approximation and other using a r-rank approximation with $r \in \{1,3,5,7\}$. The NMSE (dB) between the original matriz $\boldsymbol{X}$ and its low-rank approximations are 
    shown in the following table

    \begin{table}[ht!]
        \centering
        \begin{tabular}{|l|l|l|l|l|}
        \hline
        r = 9 & r = $7$ & r = $5$ & r = $3$ & r = $1$ \\ \hline
        -604.8023 & -51.3722 & -26.7589 & -16.9054 & -6.3068 \\ \hline
        \end{tabular}
    \end{table}

    and as we can observe the low-rank approximations are not good enought mainly because we are working with a full-rank matrix. Thus, it would be expected to obtain a better
    performance for low-rank approximations of the matrix $\boldsymbol{X}$ if the matrix would to be rank defficient.

    \subsection*{Produced Algorithm}

    \begin{verbatim}
        %% Kronecker Product Single Value Decomposition (KPSVD)

        % This function computes the LSKRF of a given matrix.   
        % Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
        % Created: March 2022

        function [U,S,V,rkp] = KPSVD(X,ia,ja,ib,jb)
            [ix,jx] = size(X);

            I = (ix/ia) + zeros(1,ia);
            J = (jx/ja) + zeros(1,ja);
            blocks_of_X = mat2cell(X,I,J);

            k = 1;
            Xhat = complex(zeros(ib*jb,ia*ja),0);
            for j = 1:ja
                for i = 1:ia
                    vec_of_block = cell2mat(blocks_of_X(i,j));
                    vec_of_block = vec_of_block(:);
                    Xhat(:,k) = vec_of_block;
                    k = k + 1;
                end
            end
            [U,S,V] = svd(Xhat');
            rkp = sum(sum(S>0));
        end

        %% ----- Homework 5 ----- %%
        clc;        % This function computes the LSKRF of a given matrix.   
        % Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
        % Created: March 2022

        function [U,S,V,rkp] = KPSVD(X,ia,ja,ib,jb)
            [ix,jx] = size(X);

            I = (ix/ia) + zeros(1,ia);
            J = (jx/ja) + zeros(1,ja);
            blocks_of_X = mat2cell(X,I,J);

            k = 1;
            Xhat = complex(zeros(ib*jb,ia*ja),0);
            for j = 1:ja
                for i = 1:ia
                    vec_of_block = cell2mat(blocks_of_X(i,j));
                    vec_of_block = vec_of_block(:);
                    Xhat(:,k) = vec_of_block;
                    k = k + 1;
                end
            end
            [U,S,V] = svd(Xhat');
            rkp = sum(sum(S>0));
        end

        r1 = 3;
        c1 = 3;
        r2 = 3;
        c2 = 3;
        rank_of_A = 3;
